\bibitem{JMarsh}
John~H.~Marsh,
\newblock "Quantum well Intermixing"
\newblock {\em Semlcond. Sci. Technol}, vol.8, pp.1136-1155, 1993.

\bibitem{IIID}
Sylvain Charbonneau, Emil S. Koteles, P. J. Poole, J. J. He, G. C.
Aers, J. Haysom, M. Buchanan, Y. Feng, A. Delage, F. Yang, M.
Davies, R. D. Goldberg, P. G. Piva, and I. V. Mitchell,
\newblock "Photonic Integrated Circuits Fabricated Using Ion Implantation"
\newblock {\em IEEE JOURNAL OF SELECTED TOPICS IN QUANTUM ELECTRONICS}, vol.4, no.4, pp.772-793, 1998.

\bibitem{IFVD}
B. S. Ooi, K. McIlvaney, M. W. Street, A. S. Helmy, S. G. Ayling, A.
C. Bryce, J. H. Marsh, and J. S. Roberts,
\newblock "Selective quantum-well intermixing in GaAsÿAlGaAs structures using impurity-free vacancy diffusion"
\newblock {\em IEEE J. Quantum Electron}, vol. 33, no. 10, pp. 1784ÿ1793, Oct. 1997.

\bibitem{SiO2}
S. P. McDougall, O. P. Kowalski, C. J. Hamilton, F. Camacho, B. Qiu,
M. Kee, R. M. De La Rue, A. C. Bryce, and J. H. Marsh,
\newblock "Monolithic integration via a universal damage enhanced quantum well intermixing technique"
\newblock {\em IEEE J. Sel. Topics Quantum Electron}, vol. 4, no. 4, pp. 636ÿ646, Jul./Aug. 1998.

\bibitem{PAID}
B. S.Ooi, T.K.Ong, andO.Gunawan,
\newblock "Multiple-wavelength integration in InGaAsÿInGaAsP structures using pulsed laser irradiation
induced quantum well intermixing"
\newblock {\em IEEE J. Quantum Electron.}, vol. 40, no. 5, pp. 481ÿ490, May 2004.

\bibitem{ArPlasma}
H. S. Djie, T. Mei, J. Arokiaraj, C. Sookdhis, S. F. Yu, L. K. Ang,
and X. H. Tang,
\newblock "Experimental and Theoretical Analysis of Argon Plasma-Enhanced Quantum-Well Intermixing"
\newblock {\em IEEE JOURNAL OF QUANTUM ELECTRONICS}, VOL. 40, NO. 2, pp.166-174, Feb. 2004

\bibitem{40G}
James~W.~Raring and Larry~A.~Coldren,
\newblock "40-Gb/s Widely Tunable Transceivers"
\newblock {\em IEEE JOURNAL OF SELECTED TOPICS IN QUANTUM ELECTRONICS}, vol.13, no.1, pp.3-14, 2007.

\bibitem{table}
\newblock {\em IEE Proc.-Optoelectron}, vol.149, no.4, August, 2002.

\bibitem{redshift}
D.~Nie, T.~Mei, X.~H.~Tang {\em et al}
\newblock "Argon plasma exposure enhanced intermixing in an undoped InGaAsP/InP quantum-well structure"
\newblock {\em J. Applied Physics}, 100, 046103, 2006

\bibitem{icpparam}
D.~Leong, H.~S.~Djie and P.~Dowd,
\newblock "A New Quantum Well Intermixing Technique Using Inductively Coupled
    Argon Plas ma on InGaAs/InGaAsP laser structures"

\bibitem{tex}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em
plus 0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\bibitem{zz}
Banerjee M, Pal S.~K.
\newblock Roughness of fuzzy set.
\newblock {\em Information Sciences}, 93:235$\sim$246, 1996.
